Pyg4ometry: a python library for the creation of Monte Carlo radiation transport physical geometries

### 2019-11-16 public/paper/pyg4ometry.tex
Particle -> radiation transport

\title{Pyg4ometry: a python library for the creation of Monte Carlo particle transport physical geometries}

@@

{\em Nature of problem(approx. 50-250 words):}\\
Creating computer readable geometry descriptions for Monte Carlo particle transport codes is a time consuming and error prone task.  \\
{\em Solution method(approx. 50-250 words):}\\
  %Describe the method solution here.
{\em Additional comments including Restrictions and Unusual features (approx. 50-250 words):}\\
  %Provide any additional comments here.
   \\

@@

%% main text
\section{Introduction} \label{sec:introduction}
There are numerous different software codes to simulate the passage of particles through material, so called particle transport (PT) programmes, these 
include MCNP \cite{Mcnp_Werner}, FLUKA \cite{Fluka_Ferrari,Fluka_Bohlen}, Geant3 \cite{Geant3_Brun} and Geant4 \cite{Geant4_Agostinelli}. 
All these codes are based on the Monte Carlo technique but each code either has a particular specialism or target user community.  PT Monte Carlo simulations 
have diverse uses, shielding calculations for radiological protection, detector performance, medical imaging and therapy and space radiation environment 
simulation are some examples. A fundamental requirement of all of the codes is to supply a computer readable description of the physical geometry that 
the particles are passing through.  The creation of geometry files is typically a very time consuming activity and the simulation validity and performance is directly 
dependent on the quality of the geometry. The requirement of a geometry system that allows the conversion between files prepared for different codes will 
enable cross checks of the physics processes in different particle transport codes. Parallel to the creation of geometry files for PT programs, usually computer assisted 
design (CAD) files exist for systems which need to be simulated in PT programmes. The fundamental geometric representations in CAD files is typically not 
amenable for PT programmes.  For these reasons it is advantageous to create a software tool that allows particle transport code users to rapidly develop 
geometry files, convert between common PT programme geometry formats and finally import CAD models.

>>>>

\title{Pyg4ometry: a python library for the creation of Monte Carlo radiation transport physical geometries}

@@

{\em Nature of problem(approx. 50-250 words):}\\
Creating computer readable geometry descriptions for Monte Carlo radiation transport codes is a time consuming and error prone task.  \\
{\em Solution method(approx. 50-250 words):}\\
  %Describe the method solution here.
{\em Additional comments including Restrictions and Unusual features (approx. 50-250 words):}\\
  %Provide any additional comments here.
   \\

@@

%% main text
\section{Introduction} \label{sec:introduction}
There are numerous different software codes to simulate the passage of particles through material, so called radiation transport (RT) programmes, these 
include MCNP \cite{Mcnp_Werner}, FLUKA \cite{Fluka_Ferrari,Fluka_Bohlen}, Geant3 \cite{Geant3_Brun} and Geant4 \cite{Geant4_Agostinelli}. 
All these codes are based on the Monte Carlo technique but each code either has a particular specialism or target user community.  RT Monte Carlo (RTMC) simulations 
have diverse uses, shielding calculations for radiological protection, detector performance, medical imaging and therapy and space radiation environment 
simulation are some examples. A fundamental requirement of all of the codes is to supply a computer readable description of the physical geometry that 
the particles are passing through.  The creation of geometry files is typically a very time consuming activity and the simulation validity and performance is directly 
dependent on the quality of the geometry. The requirement of a geometry system that allows the conversion between files prepared for different codes will 
enable cross checks of the physics processes in different particle transport codes. Parallel to the creation of geometry files for PT programs, usually computer assisted 
design (CAD) files exist for systems which need to be simulated in PT programmes. The fundamental geometric representations in CAD files is typically not 
amenable for PT programmes.  For these reasons it is advantageous to create a software tool that allows particle transport code users to rapidly develop 
geometry files, convert between common PT programme geometry formats and finally import CAD models.
